Preregistered as Code: Gender differences in Machiavellianism

### 2021-09-17 preregistration.Rmd
log changes to preregistration

This document only serves to illustrate Preregistration as Code.
We, therefore, do not discuss the results.
After we have acquired the data, we realized that we had to change the code for reading the data (see commit [6556a93](https://github.com/aaronpeikert/repro-tutorial/commit/6556a9395fcdd600b5b0c5358f92a2c6635ae360)).
We do not believe that these changes influence the results substantively.

>>>>

This document only serves to illustrate Preregistration as Code.
We, therefore, do not discuss the results.
After we have acquired the data, we realized that we had to change the code for reading the data, including recoding gender, missing values and reversed items (see commit [6556a93](https://github.com/aaronpeikert/repro-tutorial/commit/6556a9395fcdd600b5b0c5358f92a2c6635ae360) and commit [9f7ab21](https://github.com/aaronpeikert/repro-tutorial/commit/9f7ab212dfaf84a0398752a4b80cf14c71000d00)).
We do not believe that these changes influence the results substantively.
